---
title: "What is DS 2"
author: "Diana Ballesteros Gonzalez"
date: "10/9/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

## Load Dataset 
```{r}
library(p8105.datasets)
data(nyc_airbnb)

nyc_airbnb
```

## Rename/Clean some thing 
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(boro = neighbourhood_group)
```


```{r}
nyc_airbnb %>% 
  count(boro)

## View allows you to view in a new tab
nyc_airbnb %>% 
  count(boro, neighbourhood) %>%  View

```

## Some questions 
* Does rating vary by niehgborhood, room type, or both? 
* Hos is price related to other variables? 
* Where are rentals located? 
* What is the most expernsive area? What about the least? 
* Which listing has the most unfilled days?
* Which are has the highest density of listings? 
* What are some host characteristics? How many listings? What's associated with ratings? 

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_rating_neighborhood = mean(stars, na.rm = TRUE)) %>% 
  arrange(desc(mean_rating_neighborhood))

nyc_airbnb %>% 
  group_by(room_type) %>% 
  summarize(mean_rating_room_type = mean(stars, na.rm = TRUE)) %>% 
  arrange(mean_rating_room_type)

nyc_airbnb %>% 
  group_by(neighbourhood, room_type) %>% 
  summarize(mean_rating = mean(stars, na.rm = TRUE), sd(starts, na.rm = TRUE)) %>% 
  arrange(desc(neighbourhood)) %>% View
```

## How is price related to other variables? 
```{r}
nyc_airbnb %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(desc(mean_price))

nyc_airbnb %>% 
  group_by(boro, room_type) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(desc(mean_price)) 
```

## Where are rentals located? 
```{r}

library(ggridges)
library(viridis)

nyc_airbnb %>% 
  ggplot(aes(x = longitude, y = latitude, color = boro)) + 
  geom_point() + 
  scale_color_viridis(discrete = TRUE)
```

## 
```{r}
## Top and Bottom 5 neighborhood prices in BK:
nyc_airbnb %>%
 select(boro, neighbourhood, price) %>%
 filter(boro == "Brooklyn"| boro == "Manhattan") %>%
 group_by(neighbourhood) %>%
 summarize(mean_price = mean(price, na.rm = TRUE),
           median_price = median(price, na.rm = TRUE)) %>% 
 top_n(-5) %>% View

## =5 gives you the bottom 5 
nyc_airbnb %>%
 select(boro, neighbourhood, price) %>%
 filter(boro == "Manhattan") %>%
 group_by(neighbourhood) %>%
 summarize(mean_price = mean(price, na.rm = TRUE),
           median_price = median(price, na.rm = TRUE)) %>% 
 top_n(-5) %>% View

nyc_airbnb %>%
 select(boro, neighbourhood, price) %>%
 filter(boro == "Brooklyn") %>%
 group_by(neighbourhood) %>%
 summarize(mean_price = mean(price, na.rm = TRUE),
           median_price = median(price, na.rm = TRUE)) %>%
 top_n(-5) %>% View
```

## Chloropleoth (look it up)

